% nomenclature

%\newenvironment{nomenc}{\prefacesection{Nomenclature}}{}

\chapter*{Associated Publications}




{\textbf{Journal Articles}}
\begin{enumerate} 

\item  \textbf{Xie, Jie}, Towsey, Michael, Zhang, Jinglan, and Roe, Paul, Frog call classification based on enhanced features and machine learning algorithms, Applied Acoustics, Volume 113, June 2016, pp. 193-201.

This work corresponds to Chapter \ref{cha:cha4EnhancedFeature} in this thesis, which presents a combined feature set for frog call classification in trophy recordings.

\item	\textbf{Xie, Jie}, Towsey, Michael, Zhang, Jinglan, and Roe, Paul (2016) Adaptive frequency scaled wavelet packet decomposition for frog call classification.  Ecological Informatics, Volume 32, pp. 134-144.

This work corresponds to Chapter \ref{cha:cha5WaveletFeature} in this thesis, which develops a novel cepstral feature for frog call classification in both trophy and field recordings.



\item	Zhang Liang, Towsey Michael, \textbf{Xie Jie}, Zhang Jinglan, Roe Paul,  Using multi-label classification for acoustic pattern detection and assisting bird species surveys, Applied Acoustics, Volume 110, September 2016, Pages 91-98.

\item \textbf{Xie, Jie}, Towsey, Michael, Zhang, Jinglan, and Roe, Paul, Frog call classification: a survey, Artificial Intelligence Review (Accepted)


This work corresponds to Chapter \ref{cha:cha2LiteratureReview} in this thesis, which reviewed the extant literature on frog call classification.



\item \textbf{Xie, Jie}, Towsey, Michael, Zhang, Jinglan, and Roe, Paul, Classification of Frog Vocalizations using Acoustic and Visual Features, Journal of Signal Processing Systems  (Under review with small revision)






\end{enumerate}

{ \textbf{Conference Papers}}
\begin{enumerate} 

\item \textbf{Xie, Jie}, Michael Towsey, Jinglan Zhang, Paul Roe, Detecting Frog Calling Activity Based on Acoustic Event Detection and Multi-label Learning, Procedia Computer Science, Volume 80, 2016, Pages 627-638.
 
 
This work corresponds to Chapter \ref{cha:cha6MIML} in this thesis, which applied ML learning for frog call classification. 
 
 
\item \textbf{Xie, Jie}, Towsey, Michael, Zhang, Liang, Yasumiba, Kiyomi and Schwarzkopf, Lin,  Zhang, Jinglan, and Roe, Paul. Multiple-Instance Multiple-Label Learning for the Classification of Frog Calls with Acoustic Event Detection. International Conference on Image and Signal Processing. Springer International Publishing, 2016, pp 222-230.
 
This work corresponds to Chapter \ref{cha:cha7ML} in this thesis, which applies MIML learning for frog call classification. 
 
 
 
\item \textbf{Xie, Jie}, Towsey, Michael, Zhang, Liang, Zhang, Jinglan, and Roe, Paul, Feature Extraction Based on Bandpass Filtering for Frog Call Classification, International Conference on Image and Signal Processing, Springer International Publishing, 2016, pp 231-239.


\item	\textbf{Xie, Jie}, Towsey, Michael, Truskinger, Anthony, Eichinski, Philip, Zhang, Jinglan, and Roe, Paul (2015) Acoustic classification of Australian anurans using syllable features. In 2015 IEEE Tenth International Conference on Intelligent Sensors, Sensor Networks and Information Processing (ISSNIP), IEEE, Singapore, pp. 1-6.

\item	\textbf{Xie, Jie}, Towsey, Michael, Yasumiba, Kiyomi, Zhang, Jinglan, and Roe, Paul (2015) Detection of anuran calling activity in long field recordings for bio-acoustic monitoring. In 2015 IEEE Tenth International Conference on Intelligent Sensors, Sensor Networks and Information Processing (ISSNIP), IEEE, Singapore, pp. 1-6.



\item	\textbf{Xie, Jie}, Towsey, Michael, Zhang, Jinglan, and Roe, Paul (2015) Image processing and classification procedure for the analysis of Australian frog vocalisations. InProceedings of the 2nd International Workshop on Environmental Multimedia Retrieval, ACM, Shanghai, China, pp. 15-20.


\item	\textbf{Xie, Jie}, Towsey, Michael, Zhang, Jinglan, Dong, Xueyan, and Roe, Paul (2015)Application of image processing techniques for frog call classification. In IEEE International Conference on Image Processing (ICIP 2015), 27-30 September 2015, Québec City, Canada.

\item	\textbf{Xie, Jie}, Towsey, Michael, Eichinski, Philip, Zhang, Jinglan, and Roe, Paul (2015)Acoustic feature extraction using perceptual wavelet packet decomposition for frog call classification. In 2015 IEEE 11th International Conference on e-Science (e-Science), IEEE, Munich, Germany, pp. 237-242.

\item	\textbf{Xie, Jie}, Zhang, Jinglan and Roe, Paul,  “Discovering acoustic feature extraction and selection algorithms for frog vocalization monitoring with machine learning techniques”, 2015 Annual Conference of the Ecological Society of Australia. (Abstract accepted for poster presentation) 

\item	\textbf{Xie, Jie}, Zhang, Jinglan, and Roe, Paul (2015) Acoustic features for hierarchical classification of Australian frog calls. In 10th International Conference on Information, Communications and Signal Processing, 2-4 December 2015, Singapore.

\item	Dong, Xueyan, \textbf{Xie, Jie}, Towsey, Michael, Zhang, Jinglan, and Roe, Paul (2015)Generalised features for bird vocalisation retrieval in acoustic recordings. In IEEE International Workshop on Multimedia Signal Processing, 19-21 October 2015, Xiamen, China.

\end{enumerate} 
